What's in a name? On the automated topic naming of software maintenance activities

### 2010-03-06 icpc/icpc2010.tex
finsihed abs

\begin{abstract}
To have meaningful discussions about how software development is progressing, we must be able to devise appropriate labels for work topics. We can then categorize development artifacts as belonging to one or more of these topics. 
% Other approaches
In order to do this, approaches such as topic modeling and concept location rely on the automated application of machine learning algorithms to development artifacts. 
%limitations
However, these approaches neither use domain-specific knowledge to improve results, nor contextualize those results for developers.  While too much specificity can produce non-generalizable results, too little produces broad learners that do not provide much immediately useful detail. 
%introduce idea
This paper implements \emph{labelled topic extraction}, in which topics are extracted and given labels relating to a cross-project taxonomy. We focus on non-functional requirements related to software quality as a potential generalization, since there is some shared belief that these qualities apply broadly across many software systems and their development artifacts.  In our approach, we name topics based on a static ontology of non-functional requirements and software qualities; in essence, this adds context to general-purpose ontologies such as WordNet.  
%elaborate
In this paper, we discuss how we use this software development domain knowledge to better annotate topics of development that are extracted from the change log messages in configuration management systems such as CVS.  Since our taxonomy is global in scope, our results allow us to compare the relative importance of particular qualities across different projects. 
%sum up
Within the topics extracted from MySQL and MaxDB we found that non-functional requirements were common and often were trends across time. Our automated techniques can label topics with little computational overhead.

\end{abstract}

@@

\begin{figure*}
  \centering
  \includegraphics[height=.55\textheight]{small-maxdb-time-smear-plot-Equal}
  \caption{MaxDB 7.500: Labelled topics related to non-functional software qualities plotted over time, continuous topics are trends that occur across time}
  \label{fig:maxdb}
\end{figure*}

\begin{figure*}%[h]
  \centering
  \includegraphics[width=.97\textwidth]{small-mysql-time-smear-plot-Equal}
  \caption{MySQL 3.23: Labelled topics related to non-functional software qualities plotted over time, continuous topics are trends that occur across time}
  \label{fig:mysql}
\end{figure*}

>>>>

\begin{abstract}
To have meaningful discussions about how software development is progressing, we must be able to devise appropriate labels for work topics. We can then categorize development artifacts as belonging to one or more of these topics. 
% Other approaches
In order to do this, approaches such as topic modeling and concept location rely on the automated application of machine learning algorithms to development artifacts. 
%limitations
However, these approaches neither use domain-specific knowledge to improve results, nor contextualize those results for developers.  While too much specificity can produce non-generalizable results, too little produces broad learners that do not provide much immediately useful detail. 
%introduce idea
This paper implements \emph{labelled topic extraction}, in which topics are extracted and given labels relating to a cross-project taxonomy. We focus on non-functional requirements related to software quality as a potential generalization, since there is some shared belief that these qualities apply broadly across many software systems and their development artifacts.  
%In our approach, we name topics based on a static ontology of non-functional requirements and software qualities; in essence, this adds context to general-purpose ontologies such as WordNet.  
%elaborate
%We discuss how we use this software development domain knowledge to better annotate topics of development that are extracted from the change log messages in configuration management systems such as CVS. 
We evaluated our approach with an experimental study on two large-scale database projects, MySQL and MaxDB. Our results were generalizable across the two projects, showing that non-functional requirements were commonly discussed, and we identified topic trends over time. 	
%Our automated techniques can label topics with little computational overhead.  
%sum up
% Since our taxonomy is global in scope, our results allow us to compare the relative importance of particular qualities across different projects.
Our labelled topic extraction technique allowed us to devise appropriate, context-sensitive labels across these two projects, providing insight into software development activities.
\end{abstract}

@@

\begin{figure*}
  \centering
  % hi-res version
  % \includegraphics[height=.55\textheight]{maxdb-time-smear-plot-Equal}
  \includegraphics[height=.55\textheight]{small-maxdb-time-smear-plot-Equal}
  \caption{MaxDB 7.500: Labelled topics related to non-functional software qualities plotted over time, continuous topics are trends that occur across time}
  \label{fig:maxdb}
\end{figure*}

\begin{figure*}%[h]
  \centering
  % hi-res version
  % \includegraphics[width=.97\textwidth]{mysql-time-smear-plot-Equal}
  \includegraphics[width=.97\textwidth]{small-mysql-time-smear-plot-Equal}
  \caption{MySQL 3.23: Labelled topics related to non-functional software qualities plotted over time, continuous topics are trends that occur across time}
  \label{fig:mysql}
\end{figure*}
